Price of Anarchy for Mean Field Games

### 2018-07-09 PoA.tex
test hello

	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$.

@@

	Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$. Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
	\begin{equation*}
	\begin{split}
	    \text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} },\\
	    \text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t),
	\end{split}
	\end{equation*}
	which are bounded over $[0,T]$. Thus, the variance function $ v_t $ converges to some positive bounded function $ v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for every given time $t\in [0,T]$.
	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with the equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .

@@

	For the shake of simplicity, let's denote $\displaystyle \kappa_u = \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1 - \bar{s})} } $ and $\zeta_1 = r + \bar{r}(1-\bar{s})^2$.
	We expand firstly $\lambda$, $C^u$, $D^u$ and $\delta^{\pm}_u$ in terms of $b_2$, namely
	\begin{equation*}
	\begin{array}{rclcrcl}
	\frac{b_2}{b_2 + \bar{b}_2} &=& 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) &\qquad& 
	\lambda &=& \frac{\zeta_1}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \\
	C^u &=& \zeta_1 \kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) &\qquad&
	D^u &=& \zeta_1 \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) 
	\end{array}
	\end{equation*}
	and 
	\begin{IEEEeqnarray*}{rCl}
		\frac{\delta_u^{\pm}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^u}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
		&=& \frac{A^u}{b_2} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \pm \sqrt{\kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) + \mathcal{O}(b_2^{-2}) } \\
		&=& \pm \kappa_u + \left(A^u \mp \frac{\bar{b}_2}{2}\kappa_u \right) \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
	\end{IEEEeqnarray*}

@@

>>>>

	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$. Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.

@@

	Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
	\begin{equation*}
	\begin{split}
	    \text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} },\\
	    \text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t),
	\end{split}
	\end{equation*}
	which are bounded over $[0,T]$. Thus, the variance function $ v_t $ converges to some positive bounded function $ v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for every given time $t\in [0,T]$.
	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with the equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .

@@

	For the sake of simplicity, let's denote $\displaystyle \kappa_u = \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1 - \bar{s})} } $ and $\zeta_1 = r + \bar{r}(1-\bar{s})^2$.
	We expand firstly $\lambda$, $C^u$, $D^u$ and $\delta^{\pm}_u$ in terms of $b_2$, namely
	\begin{equation*}
	\begin{array}{rclcrcl}
	\frac{b_2}{b_2 + \bar{b}_2} &=& 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) &\qquad& 
	\lambda &=& \frac{\zeta_1}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \\
	C^u &=& \zeta_1 \kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) &\qquad&
	D^u &=& \zeta_1 \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) 
	\end{array}
	\end{equation*}
	and 
	\begin{IEEEeqnarray*}{rCl}
		\frac{\delta_u^{\pm}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^u}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
		&=& \frac{A^u}{b_2} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \pm \sqrt{\kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) + \mathcal{O}(b_2^{-2}) } \\
		&=& \pm \kappa_u + \left(A^u \mp \frac{\bar{b}_2}{2}\kappa_u \right) \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
	\end{IEEEeqnarray*}

@@

hello
